### 2019-09-22 1-Preamble/4-Acknowledgement/acknowledgement.tex
❤
Update link to one PhD thesis that was thanking me.

In the last few years, some friends thanked me in their own PhD thesis, and it is a pleasure to do the same, and cross-link to their own PhD thesis.
In a chronological order, I thank
%,
\href{http://jill-jenn.net/}{Jill-Jênn Vie} (\href{https://github.com/jilljenn/phd}{thesis link $\nearrow$}), \href{https://navikkumarmodi.wordpress.com/}{Navikkumar Modi} (\href{https://tel.archives-ouvertes.fr/tel-01668536/document}{$\nearrow$}), \href{https://quentinbodinier.wordpress.com/}{Quentin Bodinier} (\href{https://tel.archives-ouvertes.fr/tel-01731022/document}{$\nearrow$}), \href{https://paris-sorbonne.academia.edu/FBesson}{Florian Besson}\footnote{~Que je remercie deux fois plus que ce qu'il me remerciait dans sa propre thèse ! Pour répondre à la question, deux ans plus tard, tu remerciais Tom et moi un nombre non nul $x\in\N\cup\{+\infty\}$ satisfaisant $x=2x$, soit $x=+\infty$, et je t'en remercie $2x$ fois !}, \href{https://sites.google.com/view/guerand}{Jessica Guérand} (\href{https://www.theses.fr/s175725}{the}\href{https://www.theses.fr/s175725}{$\nearrow$}), \href{https://sites.google.com/view/ducasse/}{Romain Ducasse} (\href{https://drive.google.com/open?id=1u2oxRRimcO0jQfuYwSVwgKfcHU5DdoPK}{$\nearrow$}), \href{https://members.loria.fr/SAbelard/}{Simon Abelard} (\href{https://members.loria.fr/SAbelard/theseabelard.pdf}{$\nearrow$}), \href{http://www.cmap.polytechnique.fr/~sacchelli/}{Ludovic Sacchelli} (\href{https://tel.archives-ouvertes.fr/tel-01893068/document}{$\nearrow$}), \href{http://pages.saclay.inria.fr/claire.brecheteau/}{Claire Brécheteau} (\href{https://hal.archives-ouvertes.fr/tel-01897787/document}{$\nearrow$}), \href{http://www.i2m.univ-amu.fr/perso/damien.allonsius/}{Damien Allonsius} (\href{http://www.i2m.univ-amu.fr/perso/damien.allonsius/documents/recherche/these/Main.pdf}{$\nearrow$}), \href{https://remibonnefoi.wordpress.com/}{Rémi Bonnefoi}, and Rami Othman.

@@

% I would like to conclude these acknowledgements by a special thought toward Lola, who was of great support on a daily basis, who marvelled me by her enthusiasm and dynamism, and who comforted me with her laughs and love, in the last year.
% \textcolor{white}{I love you Lola, would you like to live with me?}
%
% Je souhaite terminer ces remerciements par une pensée toute particulière pour Lola, qui m'a soutenu quotidiennement, qui m'a émerveillé par son enthousiasme et qui m'a réconforté par son amour, durant la dernière année.
% \textcolor{white}{Je t'aime Lola, veut-tu vivre avec moi ?}
%
% \small{
    \emph{Deseo terminar este agradecimiento con un pensamiento especial para mi gatita \emph{L.}, quien me apoyó diariamente, me sorprendió con su entusiasmo y me consoló con sus risas y su amor, durante el año pasado. ¡Muchísimas gracias, gatita!}
    \textcolor{white}{$\heartsuit$ Te quiero, Lola, ¿quieres vivir conmigo?}
% }

>>>>

In the last few years, some friends thanked me in their own PhD thesis, and it is a pleasure to do the same, and cross-link to their own PhD thesis.
In a chronological order, I thank
%,
\href{http://jill-jenn.net/}{Jill-Jênn Vie} (\href{https://github.com/jilljenn/phd}{thesis link $\nearrow$}), \href{https://navikkumarmodi.wordpress.com/}{Navikkumar Modi} (\href{https://tel.archives-ouvertes.fr/tel-01668536/document}{$\nearrow$}), \href{https://quentinbodinier.wordpress.com/}{Quentin Bodinier} (\href{https://tel.archives-ouvertes.fr/tel-01731022/document}{$\nearrow$}), \href{https://paris-sorbonne.academia.edu/FBesson}{Florian Besson}\footnote{~Que je remercie deux fois plus que ce qu'il me remerciait dans sa propre thèse ! Pour répondre à la question, deux ans plus tard, tu remerciais Tom et moi un nombre non nul $x\in\N\cup\{+\infty\}$ satisfaisant $x=2x$, soit $x=+\infty$, et je t'en remercie $2x$ fois !}, \href{https://sites.google.com/view/guerand}{Jessica Guérand} (\href{https://www.theses.fr/s175725}{$\nearrow$}), \href{https://sites.google.com/view/ducasse/}{Romain Ducasse} (\href{https://drive.google.com/open?id=1u2oxRRimcO0jQfuYwSVwgKfcHU5DdoPK}{$\nearrow$}), \href{https://members.loria.fr/SAbelard/}{Simon Abelard} (\href{https://members.loria.fr/SAbelard/theseabelard.pdf}{$\nearrow$}), \href{http://www.cmap.polytechnique.fr/~sacchelli/}{Ludovic Sacchelli} (\href{https://tel.archives-ouvertes.fr/tel-01893068/document}{$\nearrow$}), \href{http://pages.saclay.inria.fr/claire.brecheteau/}{Claire Brécheteau} (\href{https://hal.archives-ouvertes.fr/tel-01897787/document}{$\nearrow$}), \href{http://www.i2m.univ-amu.fr/perso/damien.allonsius/}{Damien Allonsius} (\href{https://hal.archives-ouvertes.fr/tel-01887023/document}{$\nearrow$}), \href{https://remibonnefoi.wordpress.com/}{Rémi Bonnefoi}, and Rami Othman.
% Romain : https://www.theses.fr/s175711
% TODO: Rami Othman

@@

% I would like to conclude these acknowledgements by a special thought toward Lola, who was of great support on a daily basis, who marvelled me by her enthusiasm and dynamism, and who comforted me with her laughs and love, in the last year.
% \textcolor{white}{I love you Lola, would you like to live with me?}
%
% Je souhaite terminer ces remerciements par une pensée toute particulière pour Lola, qui m'a soutenu quotidiennement, qui m'a émerveillé par son enthousiasme et qui m'a réconforté par son amour, durant la dernière année.
% \textcolor{white}{Je t'aime Lola, veut-tu vivre avec moi ?}
%
% \small{
    \emph{Deseo terminar este agradecimiento con un pensamiento especial para mi gatita \emph{L.}, quien me apoyó diariamente, me sorprendió con su entusiasmo y me consoló con sus risas y su amor, durante el año pasado. ¡Muchísimas gracias, gatita!}
    \textcolor{white}{$\heartsuit$ Te quiero, Lola, ¿Quieres compartir tu vida conmigo?}
% }
